---
STA523 Colin Rundel 
HW1 FizzBuzz
Vivienne Xu
due 09102018
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE)
```

This program performs the following task: given a list of variables as input, prints each variable, if it is a positive integer, on their own line except: (1) for multiples of three prints "Fizz" instead of the variable; (2) for the multiples of five prints "Buzz"; (3) for multiples of fifteen prints "FizzBuzz". My implementation is composed of two parts: (1) check if the input is valid, i.e., if it contains only positive integers, and if it is invalid, print "invalid input" and stop the execution; (2) print the results according to the fizzbuzz algorithm.

### Task 1 - Implementation
Below is the implementation of Fizzbuzz.

```{r}

fizzbuzz = function(v){
  
  for(i in 1 : length(v)){
    if(!is.numeric(v[i]) || v[i] != round(v[i]) || v[i] <= 0 || is.nan(v[i])|| is.infinite(v[i])){
      stop("invalid input\n")
    }
  }
  for(i in 1 : length(v)){
    if(v[i] %% 15 == 0){
      cat("FizzBuzz")
    } else if(v[i] %% 5 == 0){
      cat("Buzz")
    } else if(v[i] %% 3 == 0){
      cat("Fizz")
    } else {
      cat(v[i])
    }
    cat("\n")
  }
}
```

### Task 2 - Validation & Testing

#### Good Inputs

```{r}
fizzbuzz(1)
fizzbuzz(3)
fizzbuzz(5)
fizzbuzz(15)

fizzbuzz(9:15)
fizzbuzz(15:9)
```


#### Bad Inputs

```{r error=TRUE}
fizzbuzz(-1)
fizzbuzz(-3)
fizzbuzz(-5)

fizzbuzz(Inf)
fizzbuzz(-Inf)

fizzbuzz("A")
fizzbuzz(1.5)
fizzbuzz(1i)
fizzbuzz(4i)
```


